Effects of CHILDREN's programs

### 2020-02-23 paper.Rnw

% in RStudio, install.packages("knitR")
% also, install all packages that appear in first code chunk in this file, i.e. in the one that looks like this
% <<LoadingPackages, include=FALSE>>=
% library(knitr)
% library(xtable)
% library(dplyr)
% library(stargazer)
% @

@@

<<LoadingPackages, include=FALSE>>=
library(knitr)
library(xtable)
library(dplyr)
library(stargazer)
@

@@

<<echo=FALSE>>=
totalGrantsDyn = readRDS("./ANALYSIS/GRAPHS/PAPER GRAPHS/totalRealSubTrend.Rds")
print(totalGrantsDyn)
@

>>>>

% in RStudio, install.packages("knitR")
% also, install all packages that appear in first code chunk in this file, i.e. in the one that looks like this
% <<LoadingPackages, include=FALSE>>=
% library(knitr)
% library(xtable)
% library(dplyr)
% library(stargazer)
% library(cowplot)
% @

@@

<<LoadingPackages, include=FALSE>>=
library(knitr)
library(xtable)
library(dplyr)
library(stargazer)
library(cowplot)
@

@@

<<echo=FALSE>>=
totalGrantsDyn = readRDS("./ANALYSIS/GRAPHS/PAPER/totalRealSubTrend.Rds")
print(totalGrantsDyn)
@
